\pkg{cubble}: An \proglang{R} Package for Organizing and Wrangling Multivariate Spatio-temporal Data

### 2023-07-03 cubble.Rmd
Changes section 3.1

## Data fusion and matching {#matching}

Matching time series from two lists is a common task in spatio-temporal data analysis. In cubble, matching based on distance and time series features can be performed using the functions `match_spatial()` and `match_temporal()`. The `match_spatial()` function finds the matched pairs in two cubble objects based on distance between sites:

>>>>

## Spatial and temporal matching {#matching}

Finding nearby locations across two spatio-temporal data sets measuring different processes is a common task in spatio-temporal data analysis. For example, we might want to related measurements obtained from weather stations and river gauge levels recorded at different locations and the goal is to find nearby river sensors that reflect the change in precipitation recorded by the weather station.

This type of problem can be generalize to matched pairs of locations accross different data sets or more generality groups of locations

or groups with a number of locations selected depending on the problem at hand. For example, we might want to find for a given weather station the closest river gauges to compare levels

For example, we might want to find a group of close stations and then use score functions to describe time series features between the series. In cubble, matching locations based on distance can be performed using the function `match_spatial()` which finds  matched groups in two cubble objects by first fiding the closests pairs and.

and matching time series features for selected locations`match_temporal()`. The `match_spatial()` function :
